\documentclass[a4paper,10pt]{article}

\input{preamble.tex}

%\title{Expressive implementation of HTM algorithms as a foundation for further analysis}
\title{Εκφραστική υλοποίηση των αλγορίθμων HTM ως βάση για περαιτέρω ανάλυση}
\author{Κωνσταντίνος Σαμαράς-Τσακίρης}
\date{2019-02-12}

\usetikzlibrary{arrows.meta,automata,decorations.pathmorphing,decorations.markings,
  backgrounds,positioning,fit,shapes.misc,
  graphs,arrows
}
\tikzset{node/.style={
    rectangle,
    minimum size= 1.2cm,
    thick, draw=black,
    top color=white!50!yellow!10!,
    bottom color=yellow!50!white!50!,
    font=\ttfamily
}}

\begin{document}
\maketitle

\section{Overview}
\begin{enumerate}
  \item Why HTM?
  - Intelligence, consciousness, emotion, feeling
  - {cerebellum->supervised, midbrain->reinforcement, cortex->unsupervised}
  \item Algorithms in flux, need a solid platform for experimentation
  \item Julia \& linear algebra (but hebbian learning not well expressed as linear algebra)
  \item Why Julia?
  \item \textit{A guiding question!} (Multivariate prediction?)
\end{enumerate}

\section{HTM Details}
\begin{itemize}
  \item Understanding HTM is a significant part of this work
\end{itemize}

\section{Implementation}
\begin{itemize}
  \item Base: previous implementations {htm.matlab, nupic}
  \item SP details (expressivity, performance)
  \item TM details
\end{itemize}

\section{Results}
\begin{itemize}
  \item A Julia package
  \item Upstream bug fixes (3)
  \item Correctness tests!
\end{itemize}

\section{Open questions}
\begin{enumerate}
  \item \textbf{Temporal noise tolerance}: Temporal pooling
  \item TP happens at sensorimotor object recognition
  \item no need for location coding in the 1D context of a time series
  \item no mechanism for continuous learning (defining object boundaries)
      \begin{itemize}
        \item surprise? (see column bursting)
      \end{itemize}
  \item TP
  \item Synapse permanence quantization / learning algos
  \item synaptic weights?
  \item TM drop synapses?
  \item Kipouridi paper!
\end{enumerate}

\end{document}
